%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Appointments}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {Research Scientist}
		{\href{https://capsule8.com/}{Capsule8}} % Organization
    {New York, NY, USA}
    {April 2018 - January 2020}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item[]{\textsc{Team Overview}: The research team is responsible for the design and implementation of the key detection capabilities of the Capsule8 product, the development
          of novel exploitation techniques, the detection of state-of-the art attacks with minimal overhead within the Capsule8 product and the support of various deployment scenarios and constraints based on customer needs.}
      \item[] {\textsc{Key Achievements}:
          \begin{itemize}
                \item Designed and implemented a high-performance filter which parses user configurations into runtime constraints for telemetry processing.
                \item Was a core contributor to the codebase of the product, re-structured core parts of the architecture to allow scalability and performance optimizations, and wrote tools for testing, automatic synthesis of documentation, and code sanity.
                \item Designed and implemented utilities to automatically configure the product in new environments and minimize false positives, which was instrumental in driving new sales for the company.
                \item Led research projects involving systems, data science and machine learning, and developed the necessary infrastructure automation to support them.
                \item Established benchmarks for performance analysis of different components of the product and deployed this benchmarking as part of the continuous integration cycle.
        \end{itemize}
    }
      \end{cvitems}
    }
\vspace{0.1in}
  \cventry
    {Research Intern}
		{\href{https://www.microsoft.com/en-us/research/lab/microsoft-research-cambridge/}{Microsoft Research}} % Organization
    {Cambridge, UK}
    {October 2017 - December 2017}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item[] {Systems and Networking Group: Developed a framework for
          large-scale network traffic analysis and prediction for the
              \href{https://www.microsoft.com/en-us/research/project/iris}{Iris Project}.}
      \end{cvitems}
    }

\vspace{0.1in}

\cventry
    {Research Intern} % Job title
		{\href{May 2017 - August 2017}{Trail of Bits}} % Organization
    {New York, NY, USA}
    {May 2017 - August 2017}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item[] {Worked on the \href{https://github.com/trailofbits/manticore}{Manticore symbolic execution engine}, adding support
          for symbolic execution of \href{https://binary.ninja/}{Binary Ninja IL}, and performed security audits.}
      \end{cvitems}
    }

\vspace{0.1in}

%---------------------------------------------------------
  \cventry
    {Research Intern} % Job title
		{\href{May 2015 - August 2015}{Symantec Corporation}} % Organization
    {Herndon, VA, USA}
    {June 2015 - August 2015}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item[] {Developed an ELF binary rewriting library for ARM. Designed and
            implemented interfaces supporting binary rewriting, injection of
              anti-debugging features, injection of new modules into an existing
              binary, as well as detection of packers and backdoors.}
      \end{cvitems}
    }


\vspace{0.1in}

%---------------------------------------------------------
  \cventry
{IT Support \& Website Administrator} % Job title
		{Greek Army (Obligatory Service)} % Organization
    {Athens, Greece} % Location
    {August 2011 - June 2012} % Date(s)
		{
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item[] {Responsible for the backup \& maintenance of the servers hosting
          the \href{http://www.mod.mil.gr/mod/en/}{website of the Greek Ministry of National Defence.}}
      \end{cvitems}
        }


\vspace{0.1in}

  \cventry
        {System Administrator \& Web Developer}
        {\href{http://www.cybex.gr/}{Cybex S.A.}}
    {Athens, Greece}
    {January 2011 - July 2011}
		{
      \begin{cvitems}
      \item[] {Responsible for the administration of the Linux server infrastructure,
          as well as the hosting and domain name registration services of the
          company.}
      \end{cvitems}
        }
%---------------------------------------------------------
  % \cventry
		% {System Administrator \& Web Developer}
		% {\href{http://www.cybex.gr/}{Cybex S.A.}}
    % {Greece}
    % {January 2011 - July 2011}
		% {}
    % {
      % \begin{cvitems} % description(s) of tasks/responsibilities
        % \item {researched means of retrieving a corresponding video based on image contents using image similarity algorithm.}
        % \item {implemented prototype that users can obtain torrent magnet links of corresponding video relevant to an image on web site.}
      % \end{cvitems}
    % }

%---------------------------------------------------------
\end{cventries}
