%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\cvsubsection{Conference Publications}
\begin{cvparagraph}
\begin{enumerate}[label=C\arabic*]
    \item \textbf{Theofilos Petsios}, Jason Zhao,  Angelos D. Keromytis, and Suman Jana.
        \href{http://www.cs.columbia.edu/~theofilos/files/papers/2017/slowfuzz.pdf}{\textit{``\slowfuzz: Automated Domain-Independent Detection of
        Algorithmic Complexity Vulnerabilities. ''}}. In
        Proceedings of the 24th ACM Conference on Computer and Communications
        Security (CCS), Dallas, TX, November 2017.\label{itm:slowfuzz}
    \item \textbf{Theofilos Petsios}, Adrian Tang, Salvatore Stolfo, Angelos D.
        Keromytis, and Suman Jana.
        \href{http://www.cs.columbia.edu/~theofilos/files/papers/2017/nezha.pdf}{\textit{``\nezha: Efficient Domain - Independent
        Differential Testing''}}. In 38th IEEE Symposium on Security and Privacy
        (S\&P), San Jose, CA, May 2017.\label{itm:nezha}
    \item Marios Pomonis,\textbf{Theofilos Petsios}, Angelos D. Keromytis,
        Michalis Polychronakis, Vasileios P. Kemerlis.
        \href{http://www.cs.columbia.edu/~theofilos/files/papers/2017/krx.pdf}
        {\textit{``\krx: Comprehensive
        Kernel Protection against Just-In-Time Code Reuse"}}. In Proceedings
        of the 12th European Conference on Computer Systems (EuroSys),
        April 2017.\label{itm:krx}
    \item \textbf{Theofilos Petsios}, Vasileios P. Kemerlis, Michalis
        Polychronakis, Angelos D. Keromytis. \href{http://www.cs.columbia.edu/~theofilos/files/papers/2015/dynaguard.pdf}{\textit{``DynaGuard: Armoring
        Canary-based Protections against Brute-force Attacks"}}. In Proceedings
        of the 31th Annual Computer Security Applications Conference (ACSAC),
        December 2015.\label{itm:dynaguard}
    \item Iasonas Polakis, George Argyros, \textbf{Theofilos Petsios},
        Suphannee Sivakorn, Angelos D. Keromytis. \href{http://www.cs.columbia.edu/~theofilos/files/papers/2015/ccs2015.pdf}{\textit{``Where’s Wally?
        Precise User Discovery Attacks in Location Proximity Services"}}. In
        Proceedings of the 22nd ACM Conference on Computer and Communications
        Security (CCS), October 2015.\label{itm:istalker}
    \item Marios Pomonis, \textbf{Theofilos Petsios}, Kangkook Jee, Michalis
        Polychronakis, and Angelos D. Keromytis. \href{http://www.cs.columbia.edu/~theofilos/files/papers/2014/intflow.pdf}{\textit{``IntFlow: Improving
        the Accuracy of Arithmetic Error Detection Using Information Flow
        Tracking"}}. In Proceedings of the 30th Annual Computer Security
        Applications Conference (ACSAC), December 2014.\label{itm:intflow}
    \item M. Lecuyer, G. Ducoffe, F. Lan, A. Papancea, \textbf{T. Petsios}, R.
        Spahn, A. Chaintreau, and R. Geambasu. \href{http://www.cs.columbia.edu/~theofilos/files/papers/2014/xray.pdf}{\textit{``XRay: Enhancing the
        Web's Transparency with Differential Correlation."}}, in Proceedings of
        the USENIX Security Symposium, August 2014.\label{itm:xray}
\end{enumerate}
\end{cvparagraph}

\pagebreak

\cvsubsection{Journal Publications}
\begin{cvparagraph}
\begin{enumerate}[label=J\arabic*]
    \item George Argyros, \textbf{Theofilos Petsios}, Suphannee Sivakorn,
        Angelos D. Keromytis, and Jason Polakis. \textit{``Evaluating the
        Privacy Guarantees of Location Proximity Services"}. In ACM
        Transactions on Privacy and Security (TOPS) (formerly known as
        TISSEC).\label{itm:istalker_tops}
    \item Marios Pomonis,\textbf{Theofilos Petsios}, Angelos D. Keromytis,
        Michalis Polychronakis, Vasileios P. Kemerlis.\textit{``Kernel
        Protection against Just-In-Time Code Reuse"}. In ACM Transactions on
        Privacy and Security (TOPS) (formerly known as
        TISSEC).\label{itm:krx_tops}
\end{enumerate}
\end{cvparagraph}

\cvsubsection{Other Publications}
\begin{cvparagraph}
\begin{enumerate}[label=O\arabic*]
    \item \textbf{Theofilos Petsios}, Adrian Tang, Dimitris Mitropoulos, Salvatore Stolfo, Angelos D Keromytis, Suman Jana. \href{https://arxiv.org/pdf/1708.09334.pdf}{\textit{``Tug-of-War: Observations on Unified Content Handling''}}, arXiv preprint arXiv:1708.09334, August 2017.
    \item George Argyros, \textbf{Theofilos Petsios}, Dimitris Mitropoulos
        Yunhui Zheng, Angelos D. Keromytis, and Junfeng Yang.
        \href{https://www.rsaconference.com/writable/files/About/towards_scalable_symbolic_execution_in_interpreted_languages.pdf}{\textit{``Towards Scalable Symbolic Execution in Interpreted Languages''}}, in RSAC Security Scholar Poster Exhibition, RSA Conference, February 2017.
        \label{itm:poster_arpegio}
\end{enumerate}
\end{cvparagraph}
