%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Teaching and Mentorship}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Columbia University}
    {Instructor, Introduction to Programming in C}
    {New York, USA}
    {Summer 2014}
    {
    \begin{cvitems}
    \item Designed and taught a three week summer intensive course for the
        \href{http://sps.columbia.edu/high-school/nyc/junior-senior-courses/introduction-programming-in-c}{School of Continuing Education} at Columbia University (Students: 16)
    \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Columbia University}
    {Teaching Assistant}
    {New York, USA}
    {Summer 2013 - Fall 2016}
    {
      \begin{cvitems} % description(s) of tasks/responsibilities
      \item {Fall 2016: Head Teaching Assistant (TA) for Network Security (Graduate level. Instr. Debbie Cook. Students: 34)}
      \item {Spring 2015: TA for Network Security (Graduate level. Instr. Debbie Cook. Students 33)}
        \item {Fall 2013: Head TA for Data Structures \& Algorithms (Undergraduate level. Instr.: Shlomo Hershkop. Students: 70)}
        \item {Spring 2013: Head TA for Advanced Programming (Undergraduate level. Instr.: Shlomo Hershkop. Students: 14)}\\
      \end{cvitems}
    }

%---------------------------------------------------------

\cventry
    {Columbia University}
    {Student Mentor}
    {New York, USA}
    {2016}
    {
      \begin{cvitems}
      \item {Fall 2016: Jason Zhao (undergraduate student). Project: Guided fuzzing for resource exhaustion bugs.}
      \item {Spring 2016: Benjamin Low (undergraduate student). Project: Towards a taxonomy of the security properties of major OSes.}
      \end{cvitems}
    }
\end{cventries}
